Top Text

### 2022-12-11 Paper.tex

	(?) This paper is used as an attempt to prove that stable diffusion is the best application out of the four, we chose. Our x value is the array of different applications that we use and the y value is the result of that (the distance) for each iteration on the road to trying to recreate an image using these applications. The intervening variable in this case would be the amount of experience using these applications.

	We have chosen an image that we find sufficiently covers all the challenging parts of recreating an image using ai art generation such as reflections and complex composition. We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (15 minutes). After each iteration we take the generated image (iteration) and add it to a list of the iterations that we created while recreating that image for that specific application (each application will thus have their own history of the process of the participants tying to recreate the image). With those sets of data, we then plug the images (each iteration) into an AI application that can give you a numerical value for how close one image is to another and see how close each iteration is to the image we are trying to recreate. this then gives us insight into how fast the application is (how efficient its technique is) and how many iterations you have to do to achieve a certain result. Once the data is gathered, we can create a graph to compare the applications more easily. The people that carried out this experiment also consisted of one novice and one experienced individual. This is to see which is the best application for each group of people and thus, the results will be conveyed on two separate graphs(one graph for each group of people). In terms of our secondary research question this method also gives us insight if we are aware of the techniques each of the ai generation applications use, we can notice if there is a pattern of success or failure with each and thus are able to compare them and see which one is the best.

@@

	We have chosen an image that we find sufficiently covers all the hard parts of recreating an image using ai art generation such as reflections and complex composition. We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (15 minutes). After each iteration we take that image and compile it into a list of the iterations for the process of recreating that image for that specific application. With those sets of data, we then run the images (each iteration) through an AI application developed by DeepAI that can give you a numerical value (distance) based on how close one image is to another, the lower the distance the closer the image. This way we can see how close each iteration is to the image we are trying to recreate.

@@

	\pagebreak
	\section{Results}

>>>>

	Our x value is the array of different applications that we use and the y value is the result of that (the distance) for each iteration on the road to trying to recreate an image using these applications. The intervening variable in this case would be the amount of experience using these applications.

	\subsubsection{Generating images}
	We have chosen an image that we find sufficiently covers all the challenging parts of recreating an image using ai art generation such as reflections and complex composition. We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (15 minutes). After each iteration we take the generated image (iteration) and add it to a list of the iterations that we created while recreating that image for that specific application (each application will thus have their own history of the process of the participants tying to recreate the image).

	\subsubsection{Scoring generated images}
	With those sets of data, we then plug the images (each iteration) into an AI application, developed by DeepAI, that can give you a numerical value for how close one image is to another and see how close each iteration is to the image we are trying to recreate. this then gives us insight into how fast the application is (how efficient its technique is) and how many iterations you have to do to achieve a certain result.

@@

	When choosing an image to compare each result to, we chose one that sufficiently covers all the hard parts of recreating an image using ai art generation such as reflections, complex composition, lighting differences and multiple objects within the image. We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (15 minutes). After each iteration we take that image and compile it into a list of the iterations for the process of recreating that image for that specific application.

	\subsection{Visualizing data}

@@

	\section{Results}

	\newpage
